My title

### 2024-11-01 paper/paper.qmd
03-test_analysis_data uploaded missing state in simulation and prediction fixed

$$
\mu_i = \alpha + \beta_1 \cdot \text{methodology}_i+ \beta_2 \cdot \mathrm{days\_since\_Biden\_Withdrawal}_i + \beta_3 \cdot \mathrm{is\_national}_i + u_{\text{state}[i]} + (v_{\text{pollster}[i]} + \gamma_{\text{pollster}[i]} \cdot \mathrm{days\_since\_Biden\_Withdrawal}_i)
$$

>>>>

$$
\mu_i = \alpha + \beta_1 \cdot \text{methodology}_i+ \beta_2 \cdot \mathrm{days\_since\_Biden\_Withdrawal}_i \\
       + \beta_3 \cdot \mathrm{is\_national}_i + u_{\text{state}[i]} + (v_{\text{pollster}[i]} + \gamma_{\text{pollster}[i]} \cdot \mathrm{days\_since\_Biden\_Withdrawal}_i)
$$
